Irt plot extra

### 2022-03-10 appendix-1.Rmd
Round-2 Feedback: Modification started

```{r shortreldata, include =F}
short.rel <- readxl::read_excel("Table_raw/LEBA_short_structure.xlsx")
short.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
```

>>>>

```{r shortreldata, include =F}
short.rel <- readxl::read_excel("Table_raw/LEBA_short_structure.xlsx")
short.rel <- short.rel %>% mutate_all(~ replace_na(.x, " "))
```

### 2022-03-10 manuscript.Rmd
Round-2 Feedback: Modification started

  - id            : "9"
    institution   : "XIMES GmbH, Vienna, Austria"
  - id            : "10"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "11"
    institution   : "Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "12"
    institution   : "Technical University of Munich, Department of Sport and Health Sciences (TUM SG), Munich, Germany"
  - id            : "13"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
  - id            : "*"
    institution   : "Joint first author"

@@

```{r cfaplot, include =F}
#This chunk holds codes to store CFA plot

png(filename="Manuscript.figures/CFAplot.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis. By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}

>>>>

  - id            : "9"
    institution   : "XIMES GmbH, Vienna, Austria"
  - id            : "10"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "11"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "12"
    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
  - id            : "13"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
  - id            : "*"
    institution   : "Joint first author"

@@

```{r cfaplot, eval=FALSE, include=FALSE}
#This chunk holds codes to store CFA plot

png(filename="Manuscript.figures/CFAplot2.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis. By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%',out.width='100%', warning=FALSE}
